---
title: "POLS 6381: Homework Template"
author: "Student Name"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE, error = FALSE,
  prompt = FALSE, comment = "",
  collapse = FALSE,
  tidy = FALSE
)
```


## 0. Loading Packages
```{r, warning=FALSE, message=FALSE}
rm(list=ls()) # Start clean: remove all objects from the workspace

## Libraries
library(tinytex); library(ggplot2); library(ggpubr); library(stargazer)
library(haven);   library(faraway); library(MASS);   library(aod)
library(lmtest);  library(dplyr);   library(AER);    library(glmx)
library(heatmapFit); library(maxLik); library(reshape2); library(foreign);library(car); 

options(scipen=100); options(digits = 4) 

## Working directory
setwd("/Users/songeunlee/Documents/GitHub/rmarkdown-homework-template")
```

## Load the Data

```{r}
# Make sure the data file is saved in the same folder as this .Rmd file
data <- read_dta("Olympics_HW.dta")

# Inspect variable names
names(data)

# Keep observations with non-missing GDP
subset <- data[complete.cases(data$GDP), ]
```

## 1. Produce a scatterplot with athletes on the horizontal axis and medals on the vertical axis.(3pts)

```{r fig.width=5, fig.height=3}
plot(subset$athletes, subset$medals, pch=16) # plot(log(athletes+1), log(medals+1), pch=16)
```

## 2. Estimate the following bivariate regression model using ordinary least squares:

\[
medals_i = \beta_0 + \beta_1 athletes_i + \epsilon_i
\]

### (a) Examine the coefficients; how does increasing the number of athletes by 1 impact the number of medals a country wins?

#### Answer: The estimated coefficient for athletes is 0.1145, which means that increasing the number of athletes by one is associated with an increase of about 0.115 medals, on average.

```{r}
# Estimate the bivariate OLS regression
model1 <- lm(medals ~ athletes, data = subset)

# Display regression results
summary(model1)

# Extract slope coefficient
coef(model1)["athletes"]
```

### (b) Examine the t statistic and the p value; is the slope coefficient statistically significant (p < .05)?

#### Answer: Yes, the slope coefficient is statistically significant. The t value is 45.60 and the p-value is less than 0.001, which is far below the 0.05 significance level. Therefore, we reject the null hypothesis that the slope coefficient equals zero.

```{r}
round(summary(model1)$coefficients, 4)
```

### (c) Examine the model fit statistics; how much of the variation in medals can be accounted for by differences in the number of athletes?

#### Answer: The R-squared value is 0.6833, which means that about 68.3% of the variation in medals can be explained by differences in the number of athletes.

```{r}
summary(model1)$r.squared
```

### (d) Add a regression line from this bivariate model to the scatterplot you produced earlier. (3pts)

#### Answer

```{r fig.width=6, fig.height=4}
plot(subset$athletes, subset$medals,
     xlab = "Number of Athletes",
     ylab = "Number of Medals",
     main = "Athletes and Medals")

abline(model1, col = "red", lwd = 2)
```

## 3. What is the correlation (r) between athletes and GDP? What is the R2 from a supplemental regression in which athletes is the dependent variable and GDP is the independent variable? (3pts)

```{r}
cor(subset$GDP, subset$athletes)
question3 <- lm(subset$athletes ~ subset$GDP)
summary(question3)
```
